knitr::opts_chunk$set(echo = TRUE)
getwd()
library(readr)
library(ggplot2)
library(cluster)
library(dplyr)
library(clustertend)
library(factoextra)
library(dendextend)
```{r setup, include=FALSE}

```

### Questions I will be working on

# which bike is  most expensive in category 1?
# which bike is least expensive in category 1?
# which frame is most expensive carbon or alumunium?
# which frame is least expensive carbon or alumunium?
# which is least expensive in category 2?
# which is most expensive in category 2 ?
```{r}

```

### importing the data set into R and uploading it
bikevendors<-read.csv("Downloads/bikeVendors.csv",header = TRUE)
```{r}

```

### removing the spaces in header of each column,this makes easier to work on dataset
names(bikevendors) <- make.names(names(bikevendors))
View(bikevendors)
```{r}

```

### looking for null or NA values in the data set
bikevendors %>% 
  select_if(function(x) any(is.na(x))) %>% 
  summarise_all(funs(sum(is.na(.)))) -> extra_NA
View(extra_NA)
```{r}

```

# it seems there is no missing value in our data set, nowe can move with our data for analysis

### looking at the dataset and understanding its factor
str(bikevendors)
```{r}

```

### summarizing the dataset and see what analysis can we come up to

summary(bikevendors)
```{r}

```

# Based on our summary we can see that the maximum price of a bike is 12790 while the cheapes one is 415
# Carbon frame seems to be the most popular one with total number of 57 while Alumunium is 40
# Mountain bike in category 1 seems to be popular with number of 51 and Road comes with 46
# The average price of bikes is 3954

### My prime focus on looking into each category and frame of bikes with respect to price

### Analysis for Category 1 bike with respect to prices
```{r}

```

bikevendors %>%
  group_by(category1) %>%
  summarize(min(price),max(price))
# The summary shows,IN CATEGORY 1 both bikes are the most expensive one sharing the same price of 12790
# However the cheapest one is Mountain Bike
```{r}

```

### Analysis for Category 2 bike with respect to prices

bikevendors %>%
  group_by(category2) %>%
  summarize(min(price),max(price))
# The summary shows,In model Cross Country Race and Elite Road are the most expensive one sharing the same price of 12790
# However the cheapest one is Sport Bike
```{r}

```

### Analysis for Frame bike with respect to prices

bikevendors %>%
  group_by(frame) %>%
  summarize(min(price),max(price))
# The summary shows,In Frame Carbon the most expensive one withe price of 12790
# However the cheapest one is Alumunium Bike frame
```{r}

```

### Analysis for Model bike with respect to prices

bikevendors %>%
  group_by(model) %>%
  summarize(min(price),max(price))
# The summary shows,In model Scalpel-Si Black Inc and Supersix evo Black Inc are the most expensive one sharing the same price of 12790
# However the cheapest one is Catalyst 4 Bike
```{r}

```

### Now i would love to visualize my data through ggplot and see what i can interpret out of it

ggplot(bikevendors, aes(x=category1, y=price, fill= category1)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")   

# category 1 box plot can be viewed with different colors
```{r}

```

ggplot(bikevendors, aes(x=category2, y=price, fill= category2)) + 
  geom_boxplot(alpha=0.2) +
  theme(legend.position="none") 

# category 2 box plot can be viewed with different colors
```{r}

```

ggplot(bikevendors, aes(x=frame, y=price, fill= frame)) + 
  geom_boxplot(alpha=0.2) +
  theme(legend.position="none")

# frame box plot can be viewed with different colors
```{r}

```

ggplot(bikevendors, aes(x = category1, y = price, color="red" ))+
  geom_point()

ggplot(bikevendors, aes(x = category2, y = price, color="red" ))+
  geom_point()

ggplot(bikevendors, aes(x = frame, y = price, color="red" ))+
  geom_point()
```{r}

```

### conducting data analysis with clustering

bv <- read.csv("Downloads/bikeVendors.csv")
View(bv)
fviz_nbclust(bv, FUN = hcut, method = "gap_stat")
gap_stat <- clusGap(bv, FUN = hcut, nstart = 25, K.max = 5, B = 50)
fviz_gap_stat(gap_stat)

print(gap_stat, method = "firstmax")
fviz_gap_stat(gap_stat)
```{r}

```

### Summary of our results

# The average price for Mountain is 4255 while the average price for Road bike is 3619
# The expensive bike in category 1 are both Mountain and Road with the price of 12790
# The cheapest bike in category 1 is Mountain with the price of 415
# The summary shows,In model Cross Country Race and Elite Road are the most expensive one sharing the same price of 12790
# However the cheapest one is Sport Bike
# The summary shows,In Frame Carbon the most expensive one withe price of 12790
# However the cheapest one is Alumunium Bike frame
# The summary shows,In model Scalpel-Si Black Inc and Supersix evo Black Inc are the most expensive one sharing the same price of 12790
# However the cheapest one is Catalyst 4 Bike
